### 2020-10-24 paper/sections/design.tex
TOMM R2 submission

Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward. {\color{revise2} In iteration t, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$. The RL agent $\phi$ generates a compresion quality level $c_t$. The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$. The framework obtains next image $x_{t+1}$ and generates next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $. The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$. Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in \ref{subsec: mechanism}  Inference-Estimation-Querying-Retraining Mechanism.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.
% and we list the parameters in Section.~\ref{Section: evaluation}.

>>>>

Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward. {\color{revise2} In iteration $t$, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$. The RL agent $\phi$ generates a compresion quality level $c_t$. The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$. Then the framework obtains the next image $x_{t+1}$ and generates the next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $. The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$. Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in the inference-estimation-querying-retraining mechanism to be discussed in Section \ref{subsec: mechanism}.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.
% and we list the parameters in Section.~\ref{Section: evaluation}.
